### 2022-08-25 main/chapter_searches.tex
begin adding notes and reference urls for frequentist section

\TODO{p-value}
Figure~\ref{fig:searches_significant}
\TODO{confidence interval}
\TODO{maximum likelihood}
\TODO{unbiased}

>>>>

\TODO{
Fisher:
criteria for estimators,
(consistency, efficiency, sufficiency)
https://royalsocietypublishing.org/doi/pdf/10.1098/rsta.1922.0009
testing, p-value,
likelihood, also ratios of p-values (here named probable errors)
https://digital.library.adelaide.edu.au/dspace/handle/2440/15169
tail area = significance
http://psychclassics.yorku.ca/Fisher/Methods/
}

\TODO{
Fisher:
``We can know nothing of the probability of hypotheses or of hypothetical
quantities.''
}

\TODO{
restrict our notion of a probability with a special case: only frequency
of random events
}

\TODO{
tossing a coin is considered random
but if instead you are presented with a coin hidden under a cloth,
no frequency interpretation --- it either is or is not heads
you are therefore denied the ability to make uncertain predictions.
more generally, you are not allowed to express an uncertainty in something
unless some random process is involved
}

\TODO{
Can keep likelihoods, but cannot compute evidence values unless the prior
has a frequency interpretation.
}

\TODO{
Its void is filled with various proposed alternatives that do have frequency
interpretations and that sometimes yield useful results.
}

\TODO{
maximum likelihood, p-values, confidence intervals, and biasedness of
estimators.
}

\TODO{maximum likelihood}
\TODO{p-value}
\TODO{p-value:
The chance of a small $p$-value is small.
This is true, but not interesting because the value of any $p$-value is small.
By construction $p$-values are uniformly distributed on the unit interval
under a given hypothesis.
The frequency of $p < 0.05$ is $5\%$, but so also is the frequency of
$0.6 < p < 0.65$.
The frequency of $p < \varepsilon$ is identical to the frequency
of $0.6 < p < 0.6 + \varepsilon$.
An appropriate choice of test statistic is therefore necessary for the
$p$-value to have meaning.
}
Figure~\ref{fig:searches_significant}
\TODO{confidence interval}
\TODO{unbiased}
